Synthesizing Symmetric Lenses

### 2018-06-29 papers/SymmetricLenses/main.tex
add random stuff in my lenssynth dir

\begin{abstract}
%% \saz{This abstract too long and doesn't get to the point quickly enough. We
%%   should tighten it up considerably.}\bcp{+1.  But not just tighten ---
%%   the whole story doesn't feel very compelling.}
%%   Users commonly need to synchronize the data shared between formats, so edits
%%   to the data in one format gets propagated to the data in the other format.
%%   Manually writing the functions for these data synchronizers is tedious and
%%   error prone. Instead of manually writing these synchronizers, bidirectional
%%   languages can be used to express \emph{lenses}, groups of synchronization
%%   functions with guarantees about round-trip behavior. While these bidirectional
%%   languages help make programming these synthesizers less error-prone, they
%%   remain difficult to program in. Synthesizing bidirectional languages allows
%%   users to use lenses without manually programming them. Current
%%   synthesizers work only on the simplest types of lenses, when the two formats
%%   describe exactly the same data; this is often not the case.

%%   Oftentimes, each format may contain information the other lacks. Such
%%   synchronization tasks are described by one of the richest classes of lenses,
%%   symmetric lenses. However, symmetric lenses in their current formulation
%%   require external\bcp{why not ``internal''?} state in the form of a \emph{complement}. This statefulness
%%   makes symmetric lenses both difficult to use and difficult to
%%   synthesize. \bcp{This paragraph seems too dense.}

%%   In this work, we reformulate\bcp{More a restriction than a reformulation.}
%%   symmetric lenses as \emph{simple symmetric 
%%     lenses}. While this formulation is less expressive than symmetric lenses, it
%%   expresses many\bcp{weak} symmetric lenses while requiring \emph{no external state}. We
%%   provide combinators for simple symmetric lenses on string data, and integrate
%%   these combinators into Boomerang\bcp{undefined} while providing full backwards compatibility.

%% \bcp{This bit feels more detailed / technical than needed for an abstract.}
%%   We develop a type-directed synthesis algorithm for generating lenses in this
%%   language from regular expressions describing the data formats. A significant
%%   technical challenge in this work arises from the fact that our target language
%%   permits synchronization between formats that don't have exactly the same data
%%   -- data in one format need not be present in the other format. This gives the
%%   synthesis algorithm much more freedom, as data can be completely unaligned
%%   (edits in one format are never propagated), completely aligned (the formats
%%   are in bijective correspondence), or anywhere in between. Under the assumption
%%   that users typically want to align as much data as possible, we provide an
%%   information theoretic metric for how much data is left unaligned based on the
%%   theory of \emph{stochastic regular expressions}. Furthermore, we use this
%%   metric to develop a greedy synthesis algorithm that tries to minimize
%%   unaligned data. We experimentally demonstrate that our algorithm can
%%   efficiently synthesize simple symmetric lenses on a variety of benchmark
%%   suites consisting of synchronizing file formats from configuration files,
%%   application-specific data storage files, and data cleaning tasks.

@@

% begin introduction
\section{Introduction}

\noindent
\dpw{XXXXXX New attempt at intro starts here}

In a big-data world, one will often find similar data stored in a
variety of different formats. For instance, electronic calendars come in iCalendar, vCalendar and h-event
formats~\cite{calendar-formats}; US taxation data can be transmitted via Tax XML (used by the US government
for e-filing) or TXF (used by TurboTax)~\cite{tax-formats}; and sewing machines can read embroidery files
transmitted as PES formats, DST formats or several others~\cite{embroidery-formats}. \dpw{Editorial comment:
Phil Wadler forced his very irritating long-form citations into the
standard format. ug. how stupid is that.}
\ksf{I like the embroidery example and I also hate the long form citations.}

One way to interconvert between these varied data formats is to use a
\emph{lens}~\cite{?}---a bi-directional
program that can transform data represented in a format $S$ to a format $T$,
and vice versa.  There are a wide variety of different kinds of lenses, but well-defined lens
languages typically come with guarantees that help ensure data is
not lost or corrupted as it is transformed back and forth between different representations.

Lens languages, like any domain-specific language, also cut down the space of
possible programs one can write, and the smaller the space of programs,
the easier it is to find the program one is looking for.  
%This feature can be a negative, if the desired transformation
%falls outside of the scope provided by the language, but can also be positive, as complex
%properties (like invertability) can be enforced automatically.
%Another advantage of reducing the
%set of programs is that doing so can facilitate program synthesis, which is essentially
%a search through the space of possible computations that can be expressed as a lens.
Recent research~\cite{optician}
has exploited this fact by demonstrating that it is possible to synthesize relatively
large, complex lenses from specifications.
In particular, given types that describe source and target formats, there are synthesis
algorithms that will find bijective lenses~\cite{optician}
for medium-sized files, such as those housing linux
application configurations.  \ksf{why medium sized?  You can have very
large files with simple format descriptions that are bijective and for
which our previous systems would have worked just fine.} Oftentimes, these algorithms find such lenses in less than
a second, and without the aid of any examples at all, with just types describing the source and
target formats.  \dpw{I would cite the ICFP paper (cite string: maina+:quotient-synthesis) as to appear but I'm not sure how to do that
without possibly violating the spirit of double-blind reviewing. ie, if it hasn't appeared yet,
how could we know the content if we aren't the authors?  Mentioning it in the 3rd person does not
seem to suffice ...} \ksf{The ICFP 2018 website lists the paper; I
think it is okay to cite it.  The reviewer can assume we contacted the
authors for a copy.  We could ask Stephanie for a ruling if we want to
be sure.  One of the principles of double blind as adopted by SIGPLAN
is not to reduce the quality of the paper; omitting this citation
woudl have that affect.}\saz{Stephanie says we should cite it in the third
person, even if that's a bit awkward, but otherwise citing it is OK.}

One of reasons these algorithms are so effective, even relative to successful synthesis projects
in other domains, is because unless the same kind of data appears in a format many times,
there simply are not very many different bijections between related data formats.  Hence,
if the synthesis algorithm can find any bijection at all, then it is very likely
to be the one the user wants.  However, there is also a price for narrowing the synthesis
domain so dramatically:  Many real data formats are almost, but not quite, bijections.
More often two related data formats have some data in common, but also contain some differences.
For instance, two related tables might share four of five columns, but not the last.  Alternately, one ad hoc
configuration
file might host some format-specific meta data, such as a date, a time or reference number, whereas the other
does not.  Indeed, in our study of Augeas~\cite{augeus}, a RedHat system that
uses lenses to edit Linux files, we found that XXXXX of YYYYY lenses were not bijective.
\dpw{fill in with accurate stats and/or more concrete (and real) compelling examples; I made up the above.
mention that the POPL paper benchmarks all had to be edited?}
Consequently, past tools that search for strict bijections will rarely be applicable in practice.

A natural way to expand the scope of such tools is to consider a more
powerful language of lenses.  In particular, \emph{symmetric
lenses}~\cite{symmetric-lenses} encompass a broad collection of bidirectional
transformations and include bijections as well as transformations that
allow each side of the transaction to retain information not present
in the other side.  If $\ell$ is a symmetric lens between formats $S$ and $T$, one can
use it to transform data from $S$ to $T$, or vice versa equally well.  A user would typically
run $\ell$ in the forwards direction (from $S$ to $T$) on a string $s$ when a user updates
$s$---executing $\ell$ in this direction will propagate those updates to $T$.
However, because data in format $T$ may contain some information not present in format $T$,
the $S \rightarrow T$ transformation will take
both a string $s \in S$ and a string $t \in T$ as arguments.
Inuitively, the lens should extract the data ``shared'' between the two formats from $s$
as it generates an output $t'$.  If $s$ is missing information, the transformation should
extract the missing components from $t$.

Initially, we hypothesized that extending the synthesis algorithms
of Miltner \ETAL~\cite{miltner+:bijective-synthesis} to operate over symmetric lenses
as opposed to bijective lenses 
would be relatively straightforward:  Simply replace one set of combinators with another
and execute a search with similar heuristics.  However, in our early,
naive attempts to do so, we ran
into two different kinds of difficulties. \dpw{I got into the weeds a little bit there.
The goal was to set up the idea that there are ``two parts'' to a symmetric
lens transformation: the information from $s$ and the information from $t$.  In
a future paragraph in the intro we are going to explain that the central heuristic
involves minimizing the information from $t$.}

The first difficulty was pragmatic:  symmetric lenses actually
usually operate over three structures, the source $S$, the target $T$ and a
complement $C$~\cite{symmetric-lenses}.
The latter object contains all the information not present in one of $S$ or $T$.  Logistically,
the complement object must be stored away somewhere and infrastructure must be developed
to manage it.  
Perhaps more relevant though, is that complements complicate specifications, even when
those specifications are just examples.  The issues is that one cannot
just give examples of source and target; one must also give guidance on how to manage
the ``hidden state.''  In order to avoid such complexities, we defined a new
variant of symmetric lenses, which we call \emph{simple symmetric lenses}.  Our new
lenses do not require complements; they only need source and target
data as inputs. \ksf{This seems magic.  Say something about how it is
possible/under what circumstances it is possible to not need a
complement?
At the price of some expressiveness, our new lenses eliminate the need
for complements; they require only source and target data as inputs.
}

In order to characterize the expressive power of simple symmetric lenses
theoretically, we prove that simple symmetric lenses
include all (and only) those symmetric lenses that satisfy
an intuitive property called \emph{forgetfulness}.  In other words, they are the
complete set of symmetric lenses that do not require a ``memory'' to retain data
from past instances of $S$ or $T$ when making a round trip.\dpw{fix that to make the intuitive
explaination sufficiently accurate}
From a pragmatic perspective, we justify our design choices by extending
the Boomerang implementation with symmetric lenses (they had never before been implemented),
applying them successfully to a range of real-world applications,
and demonstrating that they are compatible, not just with basic bijective combinators,
but with a rich set of advanced features including quotient lenses and matching lenses.

The second difficulty appears to be more fundamental\dpw{better word?}:
While the number of bijective lenses
between two related formats is often tiny, the number of symmetric lenses is often
large.  In practice, the difference in cardinality means that when a search algorithm selects the smallest
bijective lens it finds, that lens has a good chance of being the
one a user wants.  In contrast, and to our surprise, our experiments show \dpw{can we have an experiment that
shows this?} that
when a search algorithm selects the smallest symmetric lens, it typically fails
to find the lens the user wants.  The flexibity these lenses admit when it comes to
eliding information generates an explosion of possible transformations.
To disambiguate between the many possible lenses, we need
new principles for identifying the ``likely'' ones, and we need
new algorithms to search the space of program transformations using these principles.
\dpw{Were the bijective lenses chosen using a ``smaller'' criteria?  I
forget... if not edit the prior paragraph.}\dpw{Ideally, we could back up the claim
that there are many symmetric lenses and not many bijective lenses by graphing the
number of such lenses somehow.  eg, in a past synthesis paper with Steve (POPL 2016)
we graphed
the untyped terms of type $\mathsf{int}\rightarrow\mathsf{int}$.  I wonder if we can
do something similar here.}

To overcome this second difficulty, we turned to information theory
to try to find a way to characterize the likely and unlikely lenses.  Intuitively, a ``likely'' lens
is one that propagates a lot of information from source to target and also from target
back to source.  Conversely, given the source, the target is ``unlikely'' to require very much
additional information in order to reconstruct it---if it were, then one is unlikely to
be attempting to synthesize a lens between the two formats!  In order to implement
this intuition, we turn to \emph{stochastic regular expressions} (SREs).
Stochastic regular expressions define a set of strings, as do ordinary regular expressions,
but they also provide the expected distribution of strings within that set.  Such
distributions allow us to compute the amount of information gained when presented
an element of the set.  For example, the language of the SRE $a |_{0.5} b$ contains two elements
(the strings $a$ and $b$).  The probability 0.5 annotating the union indicates that both
elements are equally likely to appear.  Consequently, if we observe 
an element of that language (either $a$ or $b$), we will gain one bit of information.  Said another way,
one bit, together with the SRE, suffices to recover the string in question.
On the other hand, consider the language of the SRE $c$.
It contains just one element (the string $c$).  If we observe that our algorithm
generates $c$, we gain zero bits of information --- the string was already determined.
Hence, a lens is ``likely,'' in a technical sense, if relative to the target SRE $T$,
very little information from $t$ is required to generate it.

With SREs in hand, we develop a new algorithm for synthesizing likely lenses.
This algorithm is constructed from a pair of collaborating search procedures.
Given source and target SREs $S$ and $T$, the first algorithm searches for two \emph{related} SREs
$S'$ and $T'$ that are \emph{compatible} (a heuristic that estimates the likelihood
our second algorithm will succeed).  $S'$ and $T'$ are related in the sense
that they define the same regular sets as $S$ and $T$ (respectively) and the distribution
of strings is identical.  Indeed, we guarantee these two properties by implementing
a search procedure that obeys the star semi-ring axioms of regular expression equivalence,
and which we have proven does not alter the probability distributions of the languages.

Given the two compatible SREs,
the second algorithm uses a greedy, type-directed algorithm find a likely lens between them.
If algorithm estimates the lens it has discovered is more likely than
any future lens it can possibly find, the search will be terminated.  Otherwise,
this lens is stored away (if it is the best found so far) and the search continues with
algorithm 1 again.

We implemented this algorithm and evaluated its effectiveness on a range of benchmarks
from XXXX to YYYYY. We found that ... \dpw{give a number of two that characterize
our empirical findings.}

In summary, our central contributions are as follows:
\begin{itemize}
\item We define the space of simple symmetric lenses, which lies between asymmetric lenses and full symmetric lenses and has the useful property that they don't have any internal state.  We characterize
the simple lenses semantically as the subset of full symmetric lenses for which a ``forgetfulness''
property holds. We also analyze the gap between simple and full symmetric lenses empirically and argue that
simple ones suffice for many applications.
\item We show how to synthesize simple symmetric lenses (including all asymmetric lenses as a special case),
using a novel application of stochastic regular expressions to guide the search process.  In particular, we
show that the RE star semi-ring equivalences remain valid when their semantics are enriched by distributions.
\item We extend the Boomerang implementation with simple symmetric lenses, showing that they can easily be
combined with a rich variety of other lens extensions including quotients and matching lenses.  We evaluate
our implementation over a set of benchmarks drawn from XXXXX and demonstrate that YYYY ... numbers ....
\end{itemize}

%Such synthesis efforts
%make it easier to use lenses as programmers do not need to be familiar with the syntax
%of a new language, and even advanced users can benefit from the productivity boost.

\noindent
\dpw{XXXXXX New attempt at intro ends here}

% state of the world
\bcp{Not very compelling:}Similar data can come in varieties of formats: scheduled jobs can be stored as
cron jobs for Linux or as Scheduled Tasks for Windows; web service
resources can be provided to clients in legacy or modern formats;
calendar events can be stored in CSV files or ICS files. Oftentimes,
files should be synchronized across these formats: when I edit a task
to run more often on my Linux machine, I want this task to run more
often on my Windows machine; when I update data through a legacy API,
I want those changes to be reflected when I retrieve it through a
modern API; when I create a new calendar event in my ICS file, I want
my CSV calendar files to be updated to reflect this change.

@@

@@

\[
  \centering
  \inferrule*
  {
    \Lens \OfType \Regex \Leftrightarrow \RegexAlt\\
    \Regex \equiv \Regex'\\
    \RegexAlt \equiv \RegexAlt'
  }
  {
    \Lens \OfType \Regex' \Leftrightarrow \RegexAlt'
  }
\]
Type equivalence enables a lens of type $S \Leftrightarrow T$ to be used as a lens of type $S' \Leftrightarrow T'$ if $S$ equivalent to $S'$ and $T$ is equivalent to $T'$. Type equivalence is useful both for addressing type annotations and for
letting compositions go through.\sam{I do not understand this statement.}
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \StringAlt$ & = & $\Lens.\CreateLOf{\StringAlt}$\\
%    $\CreateL{} \App \String$ & = & $\Lens.\CreateROf{\String}$\\
%    $\PutR{} \App \StringAlt \App \String$ & = & $\Lens.\PutLOf{\StringAlt}{\String}$\\
%    $\PutL{} \App \String \App \StringAlt$ & = & $\Lens.\PutROf{\String}{\StringAlt}$
%  \end{tabular}
%\end{center}
% end ssl

@@

The language is defined like the regular expression without probability
annotations would be.  The probabilities are defined as follows:
\sam{Why in the definition of star do we multiply by $p^n * (1-p)$? I think this 
should be explained}
\begin{center}
  \begin{tabular}{rcl}
    $\ProbabilityOf{\String}{\String''}$
    & =
    & $\begin{cases*}1 & if $\String = \String''$\\ 0 & otherwise\end{cases*}$ \\

@@

    $\ProbabilityOf{\PRegexStar{\Regex}{\Probability}}{\String}$
    & =
    & $\Sigma_{\String = \String_1 \ldots \String_n}\Probability^n*(1-\Probability)*\Pi_{i=1}^n\ProbabilityOf{\Regex}{\String_i}$\\
  \end{tabular}
\end{center}

@@

Stochastic DNF regular expressions are hierarchically built, where stochastic
DNF regular expressions are lists of stochastic sequences. Stochastic sequences
themselves are lists of interleaved strings and stochastic atoms.  Stochastic
atoms are iterated stochastic DNF regular expressions.
\sam{I think we should explicitly say what sets $A, B$, $SQ, TQ$ and $DS, DT$ range over.}
\begin{center}
  \begin{tabular}{l@{\ }c@{\ }l@{\ }>{\itshape\/}r}
    % DNF_REGEX
    \Atom{},\AtomAlt{} & \GEq{} & \PRegexStar{\DNFRegex{}}{\Probability}
% & \StarAtomType{}
\\
    \Sequence{},\SequenceAlt{} & \GEq{} &
                                                       $\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n}$ 
%& \MultiConcatSequenceType{} 
\\
    \DNFRegex{},\DNFRegexAlt{} & \GEq{} & $\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}$ %& \MultiOrDNFRegexType{} 
  \end{tabular}
\end{center}

>>>>

\begin{abstract}
\saz{This abstract too long and doesn't get to the point quickly enough. We
  should tighten it up considerably.}\bcp{+1.  But not just tighten ---
  the whole story doesn't feel very compelling.}
  Users commonly need to synchronize the data shared between formats, so edits
  to the data in one format gets propagated to the data in the other format.
  Manually writing the functions for these data synchronizers is tedious and
  error prone. Instead of manually writing these synchronizers, bidirectional
  languages can be used to express \emph{lenses}, groups of synchronization
  functions with guarantees about round-trip behavior. While these bidirectional
  languages help make programming these synthesizers less error-prone, they
  remain difficult to program in. Synthesizing bidirectional languages allows
  users to use lenses without manually programming them. Current
  synthesizers work only on the simplest types of lenses, when the two formats
  describe exactly the same data; this is often not the case.

  Oftentimes, each format may contain information the other lacks. Such
  synchronization tasks are described by one of the richest classes of lenses,
  symmetric lenses. However, symmetric lenses in their current formulation
  require external\bcp{why not ``internal''?} state in the form of a \emph{complement}. This statefulness
  makes symmetric lenses both difficult to use and difficult to
  synthesize. \bcp{This paragraph seems too dense.}

  In this work, we reformulate\bcp{More a restriction than a reformulation.}
  symmetric lenses as \emph{simple symmetric 
    lenses}. While this formulation is less expressive than symmetric lenses, it
  expresses many\bcp{weak} symmetric lenses while requiring \emph{no external state}. We
  provide combinators for simple symmetric lenses on string data, and integrate
  these combinators into Boomerang\bcp{undefined} while providing full backwards compatibility.

\bcp{This bit feels more detailed / technical than needed for an abstract.}
  We develop a type-directed synthesis algorithm for generating lenses in this
  language from regular expressions describing the data formats. A significant
  technical challenge in this work arises from the fact that our target language
  permits synchronization between formats that don't have exactly the same data
  -- data in one format need not be present in the other format. This gives the
  synthesis algorithm much more freedom, as data can be completely unaligned
  (edits in one format are never propagated), completely aligned (the formats
  are in bijective correspondence), or anywhere in between. Under the assumption
  that users typically want to align as much data as possible, we provide an
  information theoretic metric for how much data is left unaligned based on the
  theory of \emph{stochastic regular expressions}. Furthermore, we use this
  metric to develop a greedy synthesis algorithm that tries to minimize
  unaligned data. We experimentally demonstrate that our algorithm can
  efficiently synthesize simple symmetric lenses on a variety of benchmark
  suites consisting of synchronizing file formats from configuration files,
  application-specific data storage files, and data cleaning tasks.

@@

% begin introduction
\section{Introduction}
% state of the world
\bcp{Not very compelling:}Similar data can come in varieties of formats: scheduled jobs can be stored as
cron jobs for Linux or as Scheduled Tasks for Windows; web service resources can
be provided to clients in legacy or modern formats; calendar events can be
stored in CSV files or ICS files. Oftentimes, files should be synchronized
across these formats: when I edit a task to run more often on my Linux machine,
I want this task to run more often on my Windows machine; when I update data
through a legacy API, I want those changes to be reflected when I retrieve it
through a modern API; when I create a new calendar event in my ICS file, I want
my CSV calendar files to be updated to reflect this change.

@@

% begin stoch-rx
% end stoch-rx

@@

\[
  \centering
  \inferrule*
  {
    \Lens \OfType \Regex \Leftrightarrow \RegexAlt\\
    \Regex \equiv \Regex'\\
    \RegexAlt \equiv \RegexAlt'
  }
  {
    \Lens \OfType \Regex' \Leftrightarrow \RegexAlt'
  }
\]
Type equivalence enables a lens of type $S \Leftrightarrow T$ to be used as a
lens of type $S' \Leftrightarrow T'$ if $S$ equivalent to $S'$ and $T$ is
equivalent to $T'$. Type equivalence is useful both for addressing type
annotations, and for making well-typed compositions.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \StringAlt$ & = & $\Lens.\CreateLOf{\StringAlt}$\\
%    $\CreateL{} \App \String$ & = & $\Lens.\CreateROf{\String}$\\
%    $\PutR{} \App \StringAlt \App \String$ & = & $\Lens.\PutLOf{\StringAlt}{\String}$\\
%    $\PutL{} \App \String \App \StringAlt$ & = & $\Lens.\PutROf{\String}{\StringAlt}$
%  \end{tabular}
%\end{center}
% end ssl

@@

The language is defined like the regular expression without probability
annotations would be.  The probabilities are defined as follows:
\begin{center}
  \begin{tabular}{rcl}
    $\ProbabilityOf{\String}{\String''}$
    & =
    & $\begin{cases*}1 & if $\String = \String''$\\ 0 & otherwise\end{cases*}$ \\

@@

    $\ProbabilityOf{\PRegexStar{\Regex}{\Probability}}{\String}$
    & =
    & $\Sigma_{\String = \String_1 \ldots \String_n}\Probability^n*(1-\Probability)*\Pi_{i=1}^n\ProbabilityOf{\Regex}{\String_i}$\\
  \end{tabular}
\end{center}
In the stochastic regular expression
$\PRegexOr{\Regex_1}{\Regex_2}{\Probability}$, the annotation \Probability
represents the likelihood the string is in $\Regex_1$. In the stochastic regular
expression $\PRegexStar{\Regex}{\Probability}$, the annotation \Probability
how much more likely having a string involving more than $n$ iterations is than
having a string involving $n$ iterations.

@@

Stochastic DNF regular expressions are hierarchically built, where stochastic
DNF regular expressions (\DNFRegex, \DNFRegexAlt) are lists of stochastic sequences. Stochastic sequences
themselves are lists of interleaved strings and stochastic atoms.  Stochastic
atoms are iterated stochastic DNF regular expressions.
\sam{I think we should explicitly say what sets $A, B$, $SQ, TQ$ and $DS, DT$ range over.}
\begin{center}
  \begin{tabular}{l@{\ }c@{\ }l@{\ }>{\itshape\/}r}
    % DNF_REGEX
    \Atom{},\AtomAlt{} & \GEq{} & \PRegexStar{\DNFRegex{}}{\Probability}
% & \StarAtomType{}
\\
    \Sequence{},\SequenceAlt{} & \GEq{} &
                                                       $\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n}$ 
%& \MultiConcatSequenceType{} 
\\
    \DNFRegex{},\DNFRegexAlt{} & \GEq{} & $\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}$ %& \MultiOrDNFRegexType{} 
  \end{tabular}
\end{center}
